---
title: "CBASS"
author: "Hugo"
date: "2024-02-15"
output: html_document
---

#Dependencies

```{r setup, include=FALSE}

library(tidyverse)
library(ggplot2)
library(ggsignif)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(drc)
library(Rmisc)
library(viridis)
library(ggplot2)
library(RColorBrewer)
library(cowplot)
```

#Files and variables

```{r}
setwd("E:/PhD_Organized/I. Science/B. Physiology and CBASS/3. CBASS/2. data_FvFm")
#### Read in pam data ###

data_raw <- read.csv("CBASS_long_data_final_ok.csv", sep =";")
data_raw
data <- subset(data_raw, day == "CBASS" & run == "AL")
### Set correct factors etc. ####

data$Treatment <- as.factor(data$Treatment)
#data$Tank <- as.numeric(data$Tank) ## needs to be integer for DRC ##
data$genotype <- as.factor(data$genotype)
#data$tank <- as.factor(data$tank)
#data$FvFm <- as.numeric(as.character(data$FvFm))


```

##Ambient light temperature stress assay ("AL")

#DRC - Dosage response curves

```{r}
Treatment <- data$Treatment
a <- ggplot(data, aes(y=FvFm, x = data$temperature, colour = Treatment)) + geom_point() + geom_smooth() + xlab("Max temperature") + ylab("Fv/Fm") +theme_cowplot(10) + theme(axis.text.y = element_text(size = 10)) + theme(axis.text.x = element_text(size = 10)) + scale_color_manual(values = c("goldenrod", "midnightblue"))
a

#### DRC (Dosage Response Curve) Fitting####
## For a priori groups ##
DRCpam = drm(FvFm ~ temperature, data = data, curveid = Treatment, fct = LL.3(names = c("Hill", "Max", "ED50")))

summary(DRCpam)
compParm(DRCpam, 'ED50')
compParm(DRCpam, 'ED50', "-")

plot(DRCpam)
points(data$temperature, data$FvFm)
abline(a=NULL, b=34.5)
ED(DRCpam, c(50))[,1]

### For each individual ###

DRCpamindo = drm(FvFm ~ temperature, data = data, curveid = genotype,
             fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamindo)
compParm(DRCpamindo, 'ed50')
compParm(DRCpamindo, 'ed50', "-")
plot(DRCpamindo)
points(data$temperature, data$FvFm)
ED(DRCpamindo, c(50))[,1]

```


#Fit to each treatment individually

```{r}

#### DRC-Control ####
DRC_control = drm(FvFm ~ temperature, data = data[data$Treatment=="Control",],
                fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRC_control)
DRC_control$coefficients[3]
ED(DRC_control, c(50))[,1]


#### DRC-shade ####
DRC_shade = drm(FvFm ~ temperature, data = data[data$Treatment=="Shade",],
               fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRC_shade)
DRC_shade$coefficients[3]

#extract ED50
CBASS_Bleach_coeff<-DRC_control$coefficients[5]
# Eilat_CBASS_coeff<-Eilat_DRC$coefficients[6]

```


#Predict data for plotting

```{r}

CBASS_Bleach_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_Bleach_pred = as.data.frame(predict(DRC_control, newdata = CBASS_Bleach_preddata, interval = 'confidence'))
CBASS_Bleach_preddata = data.frame(CBASS_Bleach_preddata, fvfm = CBASS_Bleach_pred$Prediction, Lower = CBASS_Bleach_pred$Lower, Upper = CBASS_Bleach_pred$Upper)

CBASS_Non_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_Non_pred = as.data.frame(predict(DRC_shade, newdata = CBASS_Non_preddata, interval = 'confidence'))
CBASS_Non_preddata = data.frame(CBASS_Non_preddata, fvfm = CBASS_Non_pred$Prediction, Lower = CBASS_Non_pred$Lower, Upper = CBASS_Non_pred$Upper)
```


#Plots

```{r}

levels(data$Treatment)

### Test plot with groups ####

CBASS_DRC_plot<- ggplot() +
  geom_jitter(data = data, aes(x = temperature, y = FvFm, color = Treatment), alpha = 0.5, size = 0.8, width = 0.25) +
  scale_x_continuous(limits=c(26,40), breaks=c(26,30,34,38)) +
  scale_y_continuous(limits=c(-0.1, 0.7), breaks=c(0, 0.2, 0.4, 0.6)) +
  
  geom_line(data = CBASS_Bleach_preddata, aes(x = temp, y = fvfm), color = 'goldenrod', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Bleach_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'goldenrod', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.28690, linetype="solid", color = "goldenrod", size=0.7)+
  
  geom_line(data = CBASS_Non_preddata, aes(x = temp, y = fvfm), color = 'midnightblue', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Non_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'midnightblue', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 33.94443, linetype="solid", color = "midnightblue", size=0.7)+
  
  scale_color_manual(values=c('goldenrod','midnightblue')) +
  ylab("Fv/Fm") +
  xlab("Temperature (°C)") +
  theme_half_open(10)

CBASS_DRC_plot


```

##Low light temperature stress assay ("LL")

```{r}

data2 <- subset(data_raw, run == "LL" & day == "CBASS")
### Set correct factors etc. ####

data2$Treatment <- as.factor(data2$Treatment)
#data2$Tank <- as.numeric(data2$Tank) ## needs to be integer for DRC ##
data2$genotype <- as.factor(data2$genotype)
#data2$tank <- as.factor(data2$tank)
#data2$FvFm <- as.numeric(as.character(data2$FvFm))



Treatment2 <- data2$Treatment
a <- ggplot(data2, aes(y=FvFm, x = data2$temperature, colour = Treatment)) + geom_point() + geom_smooth() + xlab("Max temperature") + ylab("Fv/Fm") +theme_cowplot(10) + theme(axis.text.y = element_text(size = 10)) + theme(axis.text.x = element_text(size = 10)) + scale_color_manual(values = c("goldenrod", "midnightblue"))
a

#### DRC (Dosage Response Curve) Fitting####
## For a priori groups ##
DRCpam = drm(FvFm ~ temperature, data = data2, curveid = Treatment, fct = LL.3(names = c("Hill", "Max", "ED50")))

summary(DRCpam)
compParm(DRCpam, 'ED50')
compParm(DRCpam, 'ED50', "-")

plot(DRCpam)
points(data2$temperature, data2$FvFm)
ED(DRCpam, c(50))[,1]

### For each individual ###

DRCpamindo = drm(FvFm ~ temperature, data = data2, curveid = genotype,
             fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamindo)
compParm(DRCpamindo, 'ed50')
compParm(DRCpamindo, 'ed50', "-")
plot(DRCpamindo)
points(data2$temperature, data2$FvFm)
ED(DRCpamindo, c(50))[,1]

#### DRC-Control ####
DRCpamBleach = drm(FvFm ~ temperature, data = data2[data2$Treatment=="Control",],
                fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamBleach)
DRCpamBleach$coefficients[3]
ED(DRCpamBleach, c(50))[,1]


#### DRC-Shade ####
DRCpamNon = drm(FvFm ~ temperature, data = data2[data2$Treatment=="Shade",],
               fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamNon)
DRCpamNon$coefficients[3]

#extract ED50
CBASS_Bleach_coeff<-DRCpamBleach$coefficients[5]
# Eilat_CBASS_coeff<-Eilat_DRC$coefficients[6]

CBASS_Bleach_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_Bleach_pred = as.data.frame(predict(DRCpamBleach, newdata = CBASS_Bleach_preddata, interval = 'confidence'))
CBASS_Bleach_preddata = data.frame(CBASS_Bleach_preddata, fvfm = CBASS_Bleach_pred$Prediction, Lower = CBASS_Bleach_pred$Lower, Upper = CBASS_Bleach_pred$Upper)

CBASS_Non_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_Non_pred = as.data.frame(predict(DRCpamNon, newdata = CBASS_Non_preddata, interval = 'confidence'))
CBASS_Non_preddata = data.frame(CBASS_Non_preddata, fvfm = CBASS_Non_pred$Prediction, Lower = CBASS_Non_pred$Lower, Upper = CBASS_Non_pred$Upper)

levels(data2$Treatment)

### Test plot with groups ####

CBASS_DRC_plot2<- ggplot() +
  geom_jitter(data = data2, aes(x = temperature, y = FvFm, color = Treatment), alpha = 0.5, size = 0.8, width = 0.25) +
  scale_x_continuous(limits=c(26,40), breaks=c(26,30,34,38)) +
  scale_y_continuous(limits=c(-0.1, 0.7), breaks=c(0, 0.2, 0.4, 0.6)) +
  
  geom_line(data = CBASS_Bleach_preddata, aes(x = temp, y = fvfm), color = 'goldenrod', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Bleach_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'goldenrod', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.847047, linetype="solid", color = "goldenrod", size=0.7)+
  
  geom_line(data = CBASS_Non_preddata, aes(x = temp, y = fvfm), color = 'midnightblue', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Non_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'midnightblue', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.720542, linetype="solid", color = "midnightblue", size=0.7)+
  
  scale_color_manual(values=c('goldenrod','midnightblue')) +
  ylab("") +
  xlab("Temperature (°C)") +
  theme_half_open(10) + theme(axis.text.y = element_text(size = 0))

CBASS_DRC_plot2

legend <- get_legend(CBASS_DRC_plot)
CBASS_DRC_plot = CBASS_DRC_plot + theme(legend.position = "none")
CBASS_DRC_plot2 = CBASS_DRC_plot2 + theme(legend.position = "none")

plot_grid(CBASS_DRC_plot, CBASS_DRC_plot2, legend, labels = c("AL", "LL"), nrow =1, rel_widths = c(3.4,3.4,1))

```

##Light stress assay ("VL")

```{r}

dataL <- subset(data_raw, run == "VL" & day == "CBASS")
### Set correct factors etc. ####

dataL$Treatment <- as.factor(dataL$Treatment)
#data2$Tank <- as.numeric(data2$Tank) ## needs to be integer for DRC ##
dataL$genotype <- as.factor(dataL$genotype)
#data2$tank <- as.factor(data2$tank)
#data2$FvFm <- as.numeric(as.character(data2$FvFm))



TreatmentL <- dataL$Treatment
a <- ggplot(dataL, aes(y=FvFm, x = dataL$light, colour = TreatmentL)) + geom_point() + geom_smooth() + xlab("Max Light") + ylab("Fv/Fm") +theme_cowplot(10) + theme(axis.text.y = element_text(size = 10)) + theme(axis.text.x = element_text(size = 10)) + scale_color_manual(values = c("goldenrod", "midnightblue"))
a

#### DRC (Dosage Response Curve) Fitting####
## For a priori groups ##
DRCpam = drm(FvFm ~ light, data = dataL, curveid = TreatmentL, fct = LL.3(names = c("Hill", "Max", "ED50")))

summary(DRCpam)
compParm(DRCpam, 'ED50')
compParm(DRCpam, 'ED50', "-")

plot(DRCpam)
points(dataL$light, dataL$FvFm)
ED(DRCpam, c(50))[,1]

### For each individual ###

DRCpamindo = drm(FvFm ~ light, data = dataL, curveid = genotype,
             fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamindo)
compParm(DRCpamindo, 'ed50')
compParm(DRCpamindo, 'ed50', "-")
plot(DRCpamindo)
points(dataL$light, dataL$FvFm)
ED(DRCpamindo, c(50))[,1]

#### DRC-Control ####
DRCpamBleach = drm(FvFm ~ light, data = dataL[dataL$Treatment=="Control",],
                fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamBleach)
DRCpamBleach$coefficients[3]
ED(DRCpamBleach, c(50))[,1]


#### DRC-Shade ####
DRCpamNon = drm(FvFm ~ light, data = dataL[dataL$Treatment=="Shade",],
               fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamNon)
DRCpamNon$coefficients[3]

#extract ED50
CBASS_Bleach_coeff<-DRCpamBleach$coefficients[5]
# Eilat_CBASS_coeff<-Eilat_DRC$coefficients[6]

CBASS_Bleach_preddata = data.frame(temp = seq(70,1800, length.out = 100))
CBASS_Bleach_pred = as.data.frame(predict(DRCpamBleach, newdata = CBASS_Bleach_preddata, interval = 'confidence'))
CBASS_Bleach_preddata = data.frame(CBASS_Bleach_preddata, fvfm = CBASS_Bleach_pred$Prediction, Lower = CBASS_Bleach_pred$Lower, Upper = CBASS_Bleach_pred$Upper)

CBASS_Non_preddata = data.frame(temp = seq(70,1800, length.out = 100))
CBASS_Non_pred = as.data.frame(predict(DRCpamNon, newdata = CBASS_Non_preddata, interval = 'confidence'))
CBASS_Non_preddata = data.frame(CBASS_Non_preddata, fvfm = CBASS_Non_pred$Prediction, Lower = CBASS_Non_pred$Lower, Upper = CBASS_Non_pred$Upper)

levels(dataL$Treatment)

### Test plot with groups ####

CBASS_DRC_plotL<- ggplot() +
  geom_jitter(data = dataL, aes(x = light, y = FvFm, color = TreatmentL), alpha = 0.5, size = 0.8, width = 0.25) +
  scale_x_continuous(limits=c(50,1850), breaks=c(100,600,1100,1600)) +
  scale_y_continuous(limits=c(-0.1, 0.7), breaks=c(0, 0.2, 0.4, 0.6)) +
  
  geom_line(data = CBASS_Bleach_preddata, aes(x = temp, y = fvfm), color = 'goldenrod', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Bleach_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'goldenrod', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 1381.889, linetype="solid", color = "goldenrod", size=0.7)+
  
  geom_line(data = CBASS_Non_preddata, aes(x = temp, y = fvfm), color = 'midnightblue', show.legend = FALSE) +
  geom_ribbon(data = CBASS_Non_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'midnightblue', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 1084.725, linetype="solid", color = "midnightblue", size=0.7)+
  
  scale_color_manual(values=c('goldenrod','midnightblue')) +
  ylab("") +
  xlab("Light intensity (µmol/m²/s)") +
  theme_half_open(10) + theme(axis.text.y = element_text(size = 0))

CBASS_DRC_plotL

CBASS_DRC_plotL = CBASS_DRC_plotL + theme(legend.position = "none")

plot_grid(CBASS_DRC_plot, CBASS_DRC_plot2, CBASS_DRC_plotL, nrow =1)

```


#Assay AL and LL together

```{r}
data3 <- subset(data_raw, day == "CBASS" & run != "VL")
### Set correct factors etc. ####

data3$Treatment <- as.factor(data3$Treatment)
#data2$Tank <- as.numeric(data2$Tank) ## needs to be integer for DRC ##
data3$genotype <- as.factor(data3$genotype)
#data2$tank <- as.factor(data2$tank)
#data2$FvFm <- as.numeric(as.character(data2$FvFm))


Run <- as.factor(data3$env_run)
Treatment3 <- data3$Treatment
a <- ggplot(data3, aes(y=FvFm, x = data3$temperature, colour = Run)) + geom_point() + geom_smooth() + xlab("Max temperature") + ylab("Fv/Fm") +theme_cowplot(10) + theme(axis.text.y = element_text(size = 10)) + theme(axis.text.x = element_text(size = 10)) + scale_color_manual(values = c("goldenrod", "goldenrod4", "blue3", "midnightblue"))
a

#### DRC (Dosage Response Curve) Fitting####
## For a priori groups ##
DRCpam = drm(FvFm ~ temperature, data = data3, curveid = Run, fct = LL.3(names = c("Hill", "Max", "ED50")))

summary(DRCpam)
compParm(DRCpam, 'ED50')
compParm(DRCpam, 'ED50', "-")


plot(DRCpam)
points(data3$temperature, data3$FvFm)
ED(DRCpam, c(50))[,1]

### For each individual ###

DRCpamindo = drm(FvFm ~ temperature, data = data3, curveid = genotype,
             fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpamindo)
compParm(DRCpamindo, 'ed50')
compParm(DRCpamindo, 'ed50', "-")
plot(DRCpamindo)
points(data3$temperature, data3$FvFm)
ED(DRCpamindo, c(50))[,1]

#### 1 DRC-Control_AL ####
DRCpam1 = drm(FvFm ~ temperature, data = data3[data3$env_run=="Control_AL",],
                fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpam1)
DRCpam1$coefficients[3]
ED(DRCpam1, c(50))[,1]


#### 2 DRC-Control_LL ####
DRCpam2 = drm(FvFm ~ temperature, data = data3[data3$env_run=="Control_LL",],
               fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpam2)
DRCpam2$coefficients[3]

#### 3 DRC-Shade_AL ####
DRCpam3 = drm(FvFm ~ temperature, data = data3[data3$env_run=="Shade_AL",],
                fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpam3)
DRCpam3$coefficients[3]
ED(DRCpam3, c(50))[,1]


#### 4 DRC-Shade_LL ####
DRCpam4 = drm(FvFm ~ temperature, data = data3[data3$env_run=="Shade_LL",],
               fct = LL.3(names = c('hill', 'max', 'ed50')))
summary(DRCpam4)
DRCpam4$coefficients[3]

#extract ED50
CBASS_Bleach_coeff<-DRCpamBleach$coefficients[5]
# Eilat_CBASS_coeff<-Eilat_DRC$coefficients[6]

CBASS_1_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_1_pred = as.data.frame(predict(DRCpam1, newdata = CBASS_1_preddata, interval = 'confidence'))
CBASS_1_preddata = data.frame(CBASS_1_preddata, fvfm = CBASS_1_pred$Prediction, Lower = CBASS_1_pred$Lower, Upper = CBASS_1_pred$Upper)

CBASS_2_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_2_pred = as.data.frame(predict(DRCpam2, newdata = CBASS_2_preddata, interval = 'confidence'))
CBASS_2_preddata = data.frame(CBASS_2_preddata, fvfm = CBASS_2_pred$Prediction, Lower = CBASS_2_pred$Lower, Upper = CBASS_2_pred$Upper)

CBASS_3_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_3_pred = as.data.frame(predict(DRCpam3, newdata = CBASS_3_preddata, interval = 'confidence'))
CBASS_3_preddata = data.frame(CBASS_3_preddata, fvfm = CBASS_3_pred$Prediction, Lower = CBASS_3_pred$Lower, Upper = CBASS_3_pred$Upper)

CBASS_4_preddata = data.frame(temp = seq(27,39, length.out = 100))
CBASS_4_pred = as.data.frame(predict(DRCpam4, newdata = CBASS_4_preddata, interval = 'confidence'))
CBASS_4_preddata = data.frame(CBASS_4_preddata, fvfm = CBASS_4_pred$Prediction, Lower = CBASS_4_pred$Lower, Upper = CBASS_4_pred$Upper)


### Test plot with groups ####

CBASS_DRC_plot3<- ggplot() +
  geom_jitter(data = data3, aes(x = temperature, y = FvFm, color = Treatment, pch = run), size = 0.8, width = 0.25) +
  scale_x_continuous(limits=c(26,40), breaks=c(26,30,34,38)) +
  scale_y_continuous(limits=c(-0.1, 0.7), breaks=c(0, 0.2, 0.4, 0.6)) +
  
  geom_line(data = CBASS_1_preddata, aes(x = temp, y = fvfm), color = 'goldenrod', show.legend = FALSE) +
  geom_ribbon(data = CBASS_1_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'goldenrod', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.28690, linetype="solid", color = "goldenrod", size=0.7)+
  
  geom_line(data = CBASS_2_preddata, aes(x = temp, y = fvfm), color = "goldenrod", lty =2, show.legend = FALSE) +
  geom_ribbon(data = CBASS_2_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = "goldenrod", linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.847047, linetype= "solid", color = "goldenrod", size=0.7)+
  
  geom_line(data = CBASS_3_preddata, aes(x = temp, y = fvfm), color = "midnightblue", show.legend = FALSE) +
  geom_ribbon(data = CBASS_3_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = "midnightblue", linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 33.94443, linetype="solid", color = "midnightblue", size=0.7)+
  
  geom_line(data = CBASS_4_preddata, aes(x = temp, y = fvfm), color = 'midnightblue', lty =2, show.legend = FALSE) +
  geom_ribbon(data = CBASS_4_preddata, aes(x = temp, ymin=Lower, ymax=Upper), color = 'midnightblue', linetype=2, alpha = 0.2) +
  geom_vline(xintercept = 35.720542, linetype="solid", color = "midnightblue", size=0.7)+
  
  scale_color_manual(values =c("goldenrod", "midnightblue")) +
  ylab("") +
  xlab("Temperature (°C)") +
  theme_bw(10) #+facet_wrap(~ genotype, ncol = 3)

CBASS_DRC_plot3


CBASS_DRC_plot = CBASS_DRC_plot + theme(legend.position = "none")
CBASS_DRC_plot2 = CBASS_DRC_plot2 + theme(legend.position = "none")

plot_grid(CBASS_DRC_plot, CBASS_DRC_plot2, legend, labels = c("AL", "LL"), nrow =1, rel_widths = c(3.4,3.4,1))


var.test(data$FvFm, data2$FvFm)
kruskal.test(data$FvFm, data2$FvFm)

```


#Genotypic and inter-assay differences

```{r}
dataCBASS <- data_raw[data_raw$day=="CBASS",]
datagen <- data_raw[data_raw$day=="CBASS",]

# Create jitter/boxplots with facets for each genotype
data3$temperature <- as.factor(data3$temperature)

ggplot(data3, aes(x = temperature, y = FvFm, fill = Run)) +
  geom_boxplot() +
  scale_fill_manual(values =c("yellow2", "springgreen3", "steelblue4", "darkorchid4"))+ theme_bw(10)+
  labs(x = "Temperature (°C)", y = "Fv/Fm") +
  facet_wrap(~ genotype, ncol = 3)
#  --> not enough statistical power to achieve convergence

# Create boxplots for each genotype in AL
data$genotype <- as.factor(data$genotype)
genbox1 <- ggplot(data, aes(x = data$genotype, y = data$FvFm, fill = genotype)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, alpha = 0.5) +
  scale_fill_viridis_d()+ theme_bw(10)+
  labs(x = "Genotype", y = "Fv/Fm") + theme(legend.position = "none") + ylim(0.0,0.8) + geom_signif(comparisons = list(c("19", "P1R2")), map_signif_level = TRUE, y_position = c(0.73), annotations = c("na"))
genbox1
# Create boxplots for each genotype in LL

genbox2 <- ggplot(data2, aes(x = data2$genotype, y = data2$FvFm, fill = genotype)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, alpha = 0.5) +
  scale_fill_viridis_d()+ theme_bw(10)+
  labs(x = "Genotype", y = "") + theme(legend.position = "none") + ylim(0.0,0.8) + geom_signif(comparisons = list(c("19", "P1R2")), map_signif_level = TRUE, y_position = c(0.73), annotations = c("na"))
genbox2

# Create overall boxplots per genotype for VL run

genbox3 <- ggplot(dataL, aes(x = dataL$genotype, y = dataL$FvFm, fill = genotype)) +
  geom_boxplot() +
  geom_jitter(width = 0.2, alpha = 0.5)+
  scale_fill_viridis_d()+ theme_bw(10)+
  labs(x = "Genotype", y = "") + theme(legend.position = "none") + ylim(0.0,0.8) + geom_signif(comparisons = list(c("19", "P1R2")), map_signif_level = TRUE, y_position = c(0.73), annotations = c("na"))
genbox3

plot_grid(genbox1, genbox2, genbox3, labels =c("A","B", "C"))


#Now wrap it up for each CBASS assay
datagen <- data_raw[data_raw$day=="CBASS",]
genbox <- ggplot(datagen, aes(x = datagen$genotype, y = datagen$FvFm, fill = genotype)) +
  geom_boxplot() +
  #geom_jitter(width = 0.2, alpha = 0.3) +
  scale_fill_viridis_d()+ theme_bw(10)+
  labs(x = "Genotype", y = "Fv/Fm") + theme(legend.position = "none") + ylim(0.0,0.8) + geom_signif(comparisons = list(c("19", "P1R2")), map_signif_level = TRUE, y_position = c(0.73), annotations = c("na")) + facet_wrap(~ run, ncol = 3)
genbox


###Stats

#AL (no differences, same for LL)


mylmAL <- lm(FvFm ~ genotype, data = data)
shapiro.test(mylmAL$residuals)
plot(mylmAL)
anova(mylmAL)
summary(mylmAL)
kruskal.test(FvFm ~ genotype, data = data2)


#AL & LL

mylm <- lm(FvFm ~ genotype, data = data3)
shapiro.test(mylm$residuals)
plot(mylm)
anova(mylm)
summary(mylm)

mylm2 <- lm(FvFm ~ genotype * temperature, data = data3)
#plot(mylm2)
#shapiro.test(mylm2$residuals)
#anova(mylm2)
#summary(mylm2)

#VL
mylm3 <- lm(FvFm ~ genotype * light, data = dataL)
#shapiro.test(mylm3$residuals)
#plot(mylm3)
#anova(mylm3)
#summary(mylm3)

```


#Mixed models

*https://m-clark.github.io/mixed-models-with-R/random_intercepts.html*
*https://ourcodingclub.github.io/tutorials/mixed-models/#ranslopes* cool one for slopes
```{r}
#####___Choose best models____####
"https://rpubs.com/EmilOWK/BMA_examples"
"https://khrc.ucsf.edu/bayesian-model-averaging-bma-variable-selection"
library(lme4)
library(lmerTest)

data_mixed <- subset(data_raw, day == "CBASS")
hist(data_mixed$FvFm)

#Normalize variables
data_mixed$light2 <- scale(data_mixed$light, center = TRUE, scale = TRUE)
data_mixed$temperature2 <- scale(data_mixed$temperature, center = TRUE, scale = TRUE)

#preliminary plot to visualize data
(prelim_plot <- ggplot(data_mixed, aes(x = data_mixed$light2, y = data_mixed$FvFm)) +
  geom_point() +
  geom_smooth(method = "lm"))
basic.lm2 <- lm(data_mixed$FvFm ~ data_mixed$light2)
plot(basic.lm2)

#Random intercept model: AIC = -693.7 avec 1|genotype
data_mixed$Treatment = factor(data_mixed$Treatment)

fvfm_mixed = lmer(FvFm ~ temperature2 + light2 + (1|tank/run/Treatment), data = data_mixed)


#fvfm_mixed = lmer(FvFm ~ temperature2 + light2 + (1|Treatment/genotype), data = data_mixed)

#fvfm_mixed = lmer(FvFm ~ temperature2 * light2 + (1|genotype), data = data_mixed, subset= Treatment=="Shade")

#fvfm_mixed = lmer(FvFm ~ temperature2 * light2 + (1|genotype), data = data_mixed, subset= Treatment=="Control")

plot(fvfm_mixed)
qqnorm(resid(fvfm_mixed))
qqline(resid(fvfm_mixed))
summary(fvfm_mixed)
anova(fvfm_mixed)
extractAIC(fvfm_mixed)


#confidence interval

confint(fvfm_mixed)
## estimates of random effects

ranef(fvfm_mixed)
coef(fvfm_mixed)

#Random slope model AIC = -691.9148 - not so applicable here

#fvfm_ranslope = lmer(FvFm ~ light2 + temperature2 + (1 + light2 |tank/run/Treatment) , data = data_mixed)


#Plot the Mixed model

(mm_plot <- ggplot(data_mixed, aes(x = tank, y = FvFm, colour = Treatment)) +
      facet_wrap(~run, nrow=1) +   # a panel for each mountain range
      geom_point(alpha = 0.5) +
      theme_half_open(10) +
      geom_line(data = cbind(data_mixed, pred = predict(fvfm_mixed)), lwd = 0.8, aes(y = pred), size = 1) +  # adding predicted line from mixed model 
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels 
  + scale_color_manual(values = c("goldenrod", "midnightblue"))
)

#Look at effect ranges
library(merTools)
predictInterval(fvfm_mixed)   # for various model predictions, possibly with new data

REsim(fvfm_mixed)             # mean, median and sd of the random effect estimates

plotREsim(REsim(fvfm_mixed)) # plot the interval estimates
predict(fvfm_mixed, re.form=NA) %>% head()
predict_with_re = predict(fvfm_mixed)
plot(predict_with_re)

```


#Tank 4 comparison

```{r}
library(ggpubr)
datatank4 <- data_raw[data_raw$day=="CBASS" & data_raw$tank =="4",]

tank4 <- ggplot(datatank4, aes(x = run, y = FvFm)) + geom_boxplot() + scale_fill_manual(values = "darkgrey") + theme_cowplot(12) +ylab("Fv/Fm in tank 4") + xlab("") +ylim(0,0.7)
tank4

lm_tank <- lm(FvFm ~ run , data = datatank4)
plot(lm_tank)
anova(lm_tank)
summary(lm_tank)
shapiro.test(lm_tank$residuals)
kruskal.test(FvFm ~ run , data = datatank4)

datatank_noAL <- data_raw[data_raw$day=="CBASS" & data_raw$tank =="4" & data_raw$run !="AL",]
lm_tank2 <- lm(FvFm ~ run , data = datatank_noAL)
shapiro.test(lm_tank2$residuals)
anova(lm_tank2)
summary(lm_tank2)
```


#Bleaching pictures

```{r}
library(png)
library(grid)
setwd('E:/PhD_Organized/Science/1. Physiology and CBASS/3. CBASS/3. Database_CBASS_pictures/Post-bleaching')
a0 <- readPNG("HL_T4.png")
a1 <- rasterGrob(a0, interpolate=TRUE)
b0 <- readPNG("LL_T4.png")
b1 <- rasterGrob(b0, interpolate=TRUE)
c0 <- readPNG("VL_T4.png")
c1 <- rasterGrob(c0, interpolate=TRUE)
plot_grid(a1,b1,c1)

```


#Final figure (need to merge both)
```{r}

plot_grid(CBASS_DRC_plot, CBASS_DRC_plot2, CBASS_DRC_plotL, genbox1, genbox2, genbox3, a1, b1, c1, nrow =3, rel_widths = c(1,1,1), rel_heights = c(1.5,1.3,1))

plot_grid(genbox, mm_plot, nrow =2, labels = c("", ""), label_size = 15, label_y = 1, rel_heights = c(1.2,1))

```

